\subsection{Delopgave 3}
Lemma 1 i afsnit 5.4.4 i [Ros] siger, at to sorterede lister med $m$ og $n$ elementer kan sammenflettes (merged) til en sorteret liste ved højst $m+n-1$ sammenligninger. 
\subsubsection{}
\textbf{Task:} Antag at \textsc{Merge} benytter $m+n-1$ sammenligninger til at sammenflette to lister med $m$ og $n$ elementer. Antag yderligere, at $n=2^k$ og vis ved induktion over $k$ (start med $k=0$), at \textsc{Mergesort} bruger præcis
	\begin{align*}
		n(\log_2(n)+1)=2^k(k+1)
	\end{align*}
sammenligninger hvis input-listen $L$ har $n=2^k$ elementer. Hvilket slags induktionsbevis brugte du?

\bigskip
\noindent
\textbf{Solution:} If we start in the base case where k = 0 we have that n = 1. When we only have one element \textsc{Mergesort} only makes one comparison to see if $l<r$. Now we have to show the following: 

\begin{equation}
    \begin{aligned}
        2^0(0+1)=1\\
        1\cdot0+1\cdot1=1
    \end{aligned}
\end{equation}

\noindent
Now for the inductive step where where our list has $k+1$ elements. When k goes up by one we double our number of elements. This means that when we split our list the first time we get to lists we k elements in each because $2^{k+1}=2\cdot2^k=2^k+2^k$, Merge sort will be called on both of these which we assume will make $2^k(k+1)$ comparisons plus we also call merge which will make $m+n-1$ comparisons. we also nkow that for $k>0$ n is an even number meaning that $m=n$. Lastly when we call mergesort on the original list we make one comparison to see if $l<r$. We can now make the follewing expression.

\begin{equation}
    \begin{aligned}
        2\cdot2^k(k+1)+2n-1+1\\
        2\cdot2^k(k+1)+2n\\
        3\cdot2^k(k+1)+2\cdot2^k\\
        2^{k+1}(k+1)+2^{k+1}\\
        2^{k+1}((k+1)+1)\\
        2^{k+1}(k+2)\\
        \blacksquare
    \end{aligned}
\end{equation}

\textbf{We used weak induction on k, but since k is doubling n we might have used string induction on n. This noods to be this needs to be researched a little more.}

\subsubsection{}
\textbf{Task:} Lav nu et induktionsbevis for, at \textsc{Mergesort} bruger mindre end eller lig med $2n\log_2(n)$ sammenligninger for alle $n\geq 2$ under samme antagelser om \textsc{Merge} som ovenfor. 
	
	Hints til opgaven: Vi bliver nødt til at lave induktion over $n$. Bemærk at en liste med $n+1$ elementer deles op i to lister med $\ceil{\frac{n+1}{2}}$ og $\floor{\frac{n+1}{2}}$ elementer i Mergesort. Desuden kan I få brug for følgende vurderinger:
	\begin{itemize}
		\item $2\floor{\frac{n+1}{2}}\log_2(\floor{\frac{n+1}{2}})\leq 2\floor{\frac{n+1}{2}}\log_2(\ceil{\frac{n+1}{2}})$
		\item $\floor{\frac{n+1}{2}}+\ceil{\frac{n+1}{2}}=\frac{n+1}{2}$
		\item $\ceil{\frac{n+1}{2}}\leq \frac{2}{3}(n+1)$ når $n$ er et positivt heltal
		\item $\log_2(\frac{2}{3}(n+1))=\log_2(n+1)-\log_2(\frac{3}{2})$
		\item $n+1-2(n+1)\log_2(\frac{3}{2})<0$ når $n$ er positiv.
	\end{itemize}	 

\bigskip
\noindent
\textbf{Solution:} Base step we have that $n=2$ and we have to show that the following is true:

\begin{equation}
    \begin{aligned}
        2(log_2(2)+1)\leq2\cdot2(log_2(2))\\
        2(1+1)\leq2\cdot(2)\\
        4\leq4
    \end{aligned}
\end{equation}

\noindent
Now for the inductive step we have to show the following:

\begin{equation}
    \begin{aligned}
        (n+1)(log_2(n+1)+1)\leq2(n+1)log_2(n+1)\\
        (n+1)log_2(n+1)+n+1\leq2(n+1)log_2(n+1)\\
        n+1\leq(n+1)log_2(n+1)\\
        \frac{n+1}{n+1}\leq\frac{(n+1)log_2(n+1)}{n+1}\\
        1\leq log_2(n+1)\\
        \blacksquare
    \end{aligned}
\end{equation}

\noindent
The last part is true because $n\geq2$

\subsubsection{}
\textbf{Task:} Hvilket slags induktionsbevis brugte du? Og hvad siger resultatet om tidskompleksiteten/store-$O$ for mergesort?

\bigskip
\noindent
\textbf{Solution:} Weak induction was used. It means that the time complexity is $O(2nlog_2(n))$. We also have that if $f_1$ is $O(x_1)$ and $f_2$ is $O(x_2)$ then $f_1\cdot f_2$ is $O(x_1\cdot x_2)$.

We have the function $2n$ and $log_2(n)$ the latter can't be shortened but the first can. 

\begin{equation}
    \begin{aligned}
        |2n|\leq C|n|\\
        |2n|\leq 3|n|\\
        (3, 0)
    \end{aligned}
\end{equation}

\noindent
Therefore we get a time complexity of $O(nlog_2(n))$.
